Sketch of DP - Bayesian Inference

### 2018-07-16 main-sketch.tex
work on section 2

  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\theta)}{\Pr(\dataobs)}

@@

$\dataobs$ is observed. Since we consider $\dataobs$ to be fixed the likelihood is a function of $\theta$.

@@

Specifically, we will consider the situation where $\theta$ represents the parameter --(informally called \emph{bias})--

@@

  \Pr(\dataobs | \theta)\equiv \theta^{\Delta \alpha}(1-\theta)^{n - \Delta \alpha}

@@

where $\Delta \alpha = \displaystyle\sum_{i=1}^{n}\mathrm{x_i}$.

@@

  \Pr(\theta|\dataobs)=\betad(\alpha + \Delta \alpha,\beta + n - \Delta \alpha)

@@

In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$ is given by a Dirichelet distribution, $\dirichlet(\vtheta)$, for $k\in\mathbf{N}$,

@@

  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a_i\in\datauni}\theta_{i}^{\Delta \alpha_i}
where $\Delta \alpha_i=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a_i}$, where in $\iverson{\cdot}$ we use

@@

  \Pr(\vtheta|\dataobs)=\dirichlet(\valpha+\Delta \valpha)

@@

\section{Problem Statement}
% When we try
% to make this distribution public, sensitive information of the data
% based on which the posterior drew from can be compromised. So, it is
% important to protect this posterior distribution. When our protection
% objective is a distribution rather than a numeric value or vector, it
% would be better to measure the accuracy by distance over
% distributions, for instance, Hellinger distance, than by numeric
% metrics like $\ell_1$-norm.
This work will show that the same mechanism can
perform differently when its accuracy is computed w.r.t to a metric
over probability measures (e.g total variation distance, or Hellinger distance)
from when the metric (e.g. $\ell_1$-norm) is over the parameters.  
\section{Technical Problem Statement}
\label{sec_bayesInfer}
The posterior belief about parameters $\xis$ is inferred from the
group of sensitive data. Because it is usually published in form of a
distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself
can relieve a lot of information about sensitive data. So, the
sensitive information we want to protect here is the posterior belief,
i.e., $Pr(\xis | \dataobs)$, rather than just a sample drew from
it\cite{foulds2016theory}. Then it will be better if we can use a
distance over two distributions to measure the accuracy than a
distance over just parameters or values when we are protecting a
distribution, for instance, Hellinger distance in our paper. When we
measure the accuracy between true posterior and protected posterior
using Hellinger distance, it would be better we can have a protection
mechanism based on Hellinger distance. However, current mechanisms are
mainly based on $l_1$ norm by Laplace mechanism
\cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we
design our exponential mechanism over Hellinger distance to protect
the whole posterior distribution.

\section{Baseline Approach - Laplace Mechanism}
\label{sec_lap}
Our baseline approach come from the algorithm designed by \citet{zhang2016differential} that adding Laplace noise (\citet{dwork2014algorithmic}) to posterior parameters to preserve privacy. They perturbed $\betad$ distribution updates and truncated at $0$ to rule out invalid $\betad$ parameters to get the protected posteriors. Here we also extend their algorithm to the case of $m$ dimensional Dirichlet distributions, where we add $(m-1)$ i.i.d. Laplace noises $\{Lap_1 , Lap_2, \cdots, Lap_{m-1} \}$ and truncate in the same way. 
%where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. 
The private posterior then will be $\dirichlet(\valpha + \Delta \valpha')$, where $\Delta \valpha'$ is the perturbed parameter updates.

>>>>

  \Pr(\theta | \dataobs) = \frac{\Pr(\dataobs | \theta) \cdot \Pr(\xis)}{\Pr(\dataobs)}

@@

\dataobs~ is observed. Since we consider \dataobs to be fixed the likelihood is a function of $\theta$.

@@

Specifically, we will consider the situation where $\theta$ represents the parameter --informally called \emph{bias}--

@@

  \Pr(\dataobs | \theta)\equiv \theta^{a}(1-\theta)^{n-a}

@@

where $a=\displaystyle\sum_{i=1}^{n}\mathrm{x_i}$.

@@

  \Pr(\theta|\dataobs)=\betad(\alpha+a,\beta+n-a)

@@

In the latter case the prior distribution over $\vtheta\in [0,1]^{k}$ is given by a Dirichelet distribution, $\dirichlet(\vtheta)$, for $k\in\mathbb{N}$,

@@

  \Pr(\dataobs|\vtheta)\equiv \displaystyle\prod_{a\in\datauni}\alpha_{a}^{z_a}
\todo{to check}\]
where $z_a=\displaystyle\sum_{i=1}^{n}\iverson{x_i=a}$, where in $\iverson{\cdot}$ we use

@@

  \Pr(\vtheta|\dataobs)=\todo{to type down}\dirichlet(\vtheta+...)

@@

\section{The Problem and Baseline approach}
We are interested in designing a mechanism for privately releasing
\emph{fully} the posterior distributions derived in section \ref{},
and not a sample from them.  It's worth noticing that the posterior
distributions are fully characterized by their parameters, and the
family (beta, Dirichlet) they belong to.  Hence, in case of the
Beta-Binomial model we are interested in releasing a private version
of the pair of parameters $(\alpha',\beta')=(\alpha+a,\beta+n-a)$, and
in the case of the Dirichlet-Multinomial model we are interested in a
private version of $\vtheta'=(\vtheta+)$.  \cite{} and \cite{} have
already attacked this problem and their solution consisted in adding
independent Laplacian noise to the parameters of the posteriors. That
is, in the case of the Beta-Binomial system the value released would
be: $(\tilde\alpha,\tilde\beta)$ where $\tilde\alpha\sim Lap(\alpha+a, \frac{2}{\epsilon})$, and
$\tilde\beta\sim Lap(\beta+n-a, \frac{2}{\epsilon})$.  Where $Lap(\mu,\nu)$
denotes a Laplacian random variable with mean $\mu$ and scale $\nu$.
This mechanism is $\epsilon$-differentially private, and the noise is
calibrated w.r.t to a sensitivity of 2 which is derived by using
$\ell_1$ norm over the pair of parameters. Indeed, considering two
adjacent\footnote{Given $\dataobs, \dataobs'\in\{0,1\}^{n}$ we say that $\dataobs$ and $\dataobs'$ are adjacent iff
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$.} data observations
$\dataobs, \dataobs'$, that, from a unique prior, give rise to two posterior
distributions, characterized by the pairs
$(\alpha',\beta')$ and $(\alpha'',\beta'')$ then
$|\alpha'-\alpha''|+|\beta'-\beta''|\leq 2$.
This argument extends similarly to the Dirichelet-Multinomial system.

\noindent Also, in previous works, the accuracy has been measured again with respect to
$\ell_1$ norm. That is, an upper bound has been given to
\[
  \Pr[|\alpha - \tilde\alpha| + |\beta - \tilde\beta |\geq \gamma ]
\]
where $(\alpha, \beta), (\tilde\alpha,\tilde\beta)$ are as  defined above.
In this work we will use a metric based on a different norm to compute the sensitivity
and provide guarantees on the accuracy. In particular we will consider a metric
over probability measures and not over the parameters that represent them.
Specifically, we will use the Hellinger distance, which for two beta distributions
$\betad(\alpha_1, \beta_1), \betad(\alpha_2, \beta_2)$ is defined as
\[
  \hellinger()\equiv\todo{to type down}
\]
The same change of metric will be applied to the experimental accuracy guarantees.
\section{Technical Problem Statement}
\label{sec_bayesInfer}
The posterior belief about parameters $\xis$ is inferred from the
group of sensitive data. Because it is usually published in form of a
distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself
can relieve a lot of information about sensitive data. So, the
sensitive information we want to protect here is the posterior belief,
i.e., $Pr(\xis | \dataobs)$, rather than just a sample drew from
it\cite{foulds2016theory}. Then it will be better if we can use a
distance over two distributions to measure the accuracy than a
distance over just parameters or values when we are protecting a
distribution, for instance, Hellinger distance in our paper. When we
measure the accuracy between true posterior and protected posterior
using Hellinger distance, it would be better we can have a protection
mechanism based on Hellinger distance. However, current mechanisms are
mainly based on $l_1$ norm by Laplace mechanism
\cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we
design our exponential mechanism over Hellinger distance to protect
the whole posterior distribution.

\section{Baseline Approach - Laplace Mechanism}
\label{sec_lap}
Based on the posterior results from Bayesian inference, we calculate the Laplace mechanism updates on posterior and get the private results under Laplace mechanism. In the case of $m$ dimension Dirichlet distribution, we will add $(m-1)$ i.i.d. Laplace noises $\{| Lap_1 |, | Lap_2 |, \cdots, | Lap_{m-1} |\}$ to the output, where $Lap_i = floor(Y)$, $Y \sim Lap(\frac{2}{\epsilon})$. The private posterior then will be $\dirichlet(\alpha_1 + n_1 + | Lap_1 |, \alpha_2 + n_2 + | Lap_2 |, \cdots, \alpha_m + n - (Lap_1 + \cdots + Lap_{m-1}))$.
